*Platynereis dumerilii* three-day-old connectome --- cell-type compendium

### 2024-10-21 supplements/celltype_compendium_website/index.qmd
cell type compendium: add muscle cells

```{r}
#| echo: false
#eyespot-pigment-cell
annot <- ("celltype_non_neuronal10")
plot_cell_name(annot, "pigment cell")
plot_cell_chars(annot, "pigment cell")
"Motoneuron"

@@

```{r}
#| echo: false
#	eye-pigment-cell
annot <- ("celltype_non_neuronal11")
plot_cell_name(annot, "pigment cell")
plot_cell_chars(annot, "pigment cell")
"Motoneuron"

@@

```{r}
#| echo: false
#	vacuolar-cell-head
annot <- ("celltype_non_neuronal33")
plot_cell_name(annot, "pigment cell")
plot_cell_chars(annot, "pigment cell")
"Motoneuron"

@@

>>>>

```{r}
#| echo: false
#eyespot-pigment-cell
annot <- ("celltype_non_neuronal10")
plot_cell_name(annot, "pigment cell")
plot_cell_chars(annot, "pigment cell")

@@

```{r}
#| echo: false
#	eye-pigment-cell
annot <- ("celltype_non_neuronal11")
plot_cell_name(annot, "pigment cell")
plot_cell_chars(annot, "pigment cell")

@@

```{r}
#| echo: false
#	vacuolar-cell-head
annot <- ("celltype_non_neuronal33")
plot_cell_name(annot, "pigment cell")
plot_cell_chars(annot, "pigment cell")

@@

```{r}
#| echo: false
annot <- ("celltype_non_neuronal37")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal37.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal37.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal38")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal38.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal38.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal39")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal39.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal39.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal40")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal40.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal40.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal41")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal41.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal41.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal42")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal42.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal42.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal43")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal43.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal43.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal44")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal44.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal44.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal45")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal45.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal45.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal46")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal46.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal46.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal47")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal47.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal47.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal48")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal48.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal48.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal49")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal49.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal49.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal50")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal50.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal50.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal51")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal51.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal51.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal52")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal52.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal52.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal53")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal53.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal53.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal54")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal54.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal54.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal55")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal55.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal55.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal56")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal56.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal56.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal57")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal57.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal57.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal58")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal58.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal58.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal59")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal59.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal59.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal60")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal60.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal60.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal61")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal61.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal61.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal62")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal62.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal62.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal63")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal63.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal63.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal64")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal64.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal64.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal65")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal65.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal65.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal66")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal66.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal66.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal67")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal67.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal67.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal68")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal68.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal68.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal69")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal69.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal69.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal70")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal70.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal70.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal71")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal71.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal71.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal72")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal72.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal72.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal73")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal73.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal73.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal74")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal74.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal74.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal75")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal75.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal75.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal76")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal76.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal76.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal77")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal77.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal77.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal78")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal78.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal78.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal79")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal79.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal79.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal80")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal80.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal80.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal81")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal81.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal81.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal82")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal82.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal82.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal83")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal83.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal83.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal84")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal84.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal84.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal85")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal85.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal85.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal86")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal86.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal86.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal87")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal87.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal87.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal88")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal88.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal88.html){target="_blank"}

```{r}
#| echo: false
annot <- ("celltype_non_neuronal89")
plot_cell_name(annot, "muscle")
plot_cell_chars(annot, "muscle")
```
![](snapshots/celltype_non_neuronal89.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype_non_neuronal89.html){target="_blank"}
